Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-08 CAs_operads.tex
Dessins partie 3 (1/2)

Let us describe the normal forms for arity $n\geq 11$. For that, we
consider the following "zig-zag" of degree $k \geq 0$
\Todo{Dessins}
\begin{equation}
  z_k :=.
\end{equation}
For instance, $z_3$ and $z_4$ are the following trees
\begin{equation}
.
\end{equation}
The normal forms are decomposed into two families.
The first family is the set of the $n-1$ trees
$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$,
pictured as follows
\begin{equation}\label{equ:normal_forms_type_A}
   z_k \circ_{k+1} z_{n-1-k} = dessin.
\end{equation}
The second family is composed of the following four trees
\begin{equation}\label{equ:normal_forms_type_B}
  \RComb{n-1}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node(9)at(6,-6.75){};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](7)--(9);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node(1)at(1.00,-2.25){};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](1)--(3);
    \draw[Edge](7)--(9);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-3\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](7)--(9);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}.
\end{equation}
Indeed, each of these $n+3$ trees avoids the left membres of the
convergent presentation given in
Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}. Moreover, we have the
following.
\medbreak

>>>>

Let us describe the normal forms for arity $n\geq 11$. For that, we
consider the following "zig-zag" of degree $k \geq 0$
\Todo{Dessins}
\begin{equation}
  z_k := \Product \circ_1 ( \Product \circ_2 ( \Product 
  \circ_1 ( \Product \circ_2 \cdots
  \Product ) \cdots ).
\end{equation}
For instance, $z_4$ and $z_5$ are the following trees
\begin{equation}
	\begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
		\node(0)at(0.00,-3.60){};
		\node(2)at(2.00,-7.20){};
		\node(4)at(4.00,-7.20){};
		\node(6)at(6.00,-5.40){};
		\node(8)at(8.00,-1.80){};
		\node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
		\node[NodeST](3)at(3.00,-5.40){\begin{math}\Product\end{math}};
		\node[NodeST](5)at(5.00,-3.60){\begin{math}\Product\end{math}};
		\node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
		\draw[Edge](1)--(7);
		\draw[Edge](3)--(5);
		\draw[Edge](5)--(1);
		\node(r)at(7.00,1.35){};
		\draw[Edge](r)--(7);
	\qquad \mbox{and} \qquad
	\begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
		\node(0)at(0.00,-3.67){};
		\node(10)at(10.00,-1.83){};
		\node(2)at(2.00,-7.33){};
		\node(4)at(4.00,-9.17){};
		\node(6)at(6.00,-9.17){};
		\node(8)at(8.00,-5.50){};
		\node[NodeST](1)at(1.00,-1.83){\begin{math}\Product\end{math}};
		\node[NodeST](3)at(3.00,-5.50){\begin{math}\Product\end{math}};
		\node[NodeST](5)at(5.00,-7.33){\begin{math}\Product\end{math}};
		\node[NodeST](7)at(7.00,-3.67){\begin{math}\Product\end{math}};
		\node[NodeST](9)at(9.00,0.00){\begin{math}\Product\end{math}};
		\draw[Edge](1)--(9);
		\draw[Edge](3)--(7);
		\draw[Edge](5)--(3);
		\draw[Edge](7)--(1);
		\node(r)at(9.00,1.38){};
	\end{tikzpicture}.
\end{equation}
The normal forms are decomposed into two families.
The first family is the set of the $n-1$ trees
$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$,
pictured as follows
\begin{equation}\label{equ:normal_forms_type_A}
   z_k \circ_{k+1} z_{n-1-k} = dessin.
\end{equation}
The second family is composed of the following four trees
\begin{equation}\label{equ:normal_forms_type_B}
  \RComb{n-1}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node(9)at(6,-6.75){};
    \draw[Edge](1)--(3);
    \draw[Edge, dotted](7)--(3);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node(1)at(1.00,-2.25){};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](1)--(3);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-3\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](1)--(3);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}.
\end{equation}
Indeed, each of these $n+3$ trees avoids the left membres of the
convergent presentation given in
Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}. Moreover, we have the
following.
